### 2021-12-12 documentos/pce.tex
dandole

\section{PCE Maps} 
In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed for.
\subsection{Quantum channels} % {{{
Quantum channels comprehend the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
their construction and properties, first let us define several objects. We will
denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

@@

It can be seen from Kraus decomposition that quantum channels preserve
hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings}, defined as 
\begin{equation}
\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known \textit{Pauli basis},
%
$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
%

@@

% }}}
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
\pce{} maps are defined as those valid quantum channels that \textit{nullify} \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, in the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\end{equation}
Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\end{equation}
where $\tau_k$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
\end{align}
where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These channels can be pictured with one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$. They form a tetrahedron in the space of eigenvalues 
% }}}
\subsection{Pauli component erasing maps} % {{{

>>>>

\section{PCE Maps} 
In this section we introduce the definition of Pauli component erasing maps, but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} % {{{
Quantum channels comprehend the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
their construction and properties, first let us define several objects. We will
denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
$\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

@@

It can be seen from Kraus decomposition that quantum channels preserve
hermiticity, this has a practical consequence when using hermitian bases, \ie{} let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then the entries of the matrix representation of the quantum channel $\mcE$, $\hat
\mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular, in this work we are interested in systems of $N$ qubits, and we use hermitian bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui introduzco el nombre estandar}, defined as 
\begin{equation}
\sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known \textit{Pauli basis},
%
$1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
%

@@

% }}}
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
\pce{} maps are defined as those quantum channels that \textit{nullify} Pauli strings. In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\end{equation}
Therefore, maps erasing components of $\vec r$ are parametrized in the following way,
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\end{equation}
where $\tau_k$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
1+\tau_i-\tau_j-\tau_k &\geq 0 \ \ \forall i\neq j \neq k,
\end{align}
where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These operations can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.
These operations have been studied in \cite{Ziman2005,davalosdivisibility} and are by definition diagonal in the Pauli basis, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$. They form a tetrahedron in the space of eigenvalues 
% }}}
\subsection{Pauli component erasing maps} % {{{
